Contextual Combinatorial Cascading Bandits

### 2015-12-21 contextual combinatorial cascading bandits.tex
update lower bound discussion

\subsection{Proof of Theorem~\ref{thm:main}}

>>>>

\subsection{Lower Bounds}

Suppose we have such a graph: 
$$
	\xymatrix{
		S_0 \ar[r]^{0.8} \ar[d]_{0.9} & B \ar[dr]^{0.8} &\\
		C \ar[r]_{0.8} & D \ar[r]_{0.7} &S_1 
	}
$$
There are two paths in this graph: $A_1 = \{S_0 \to B \to S_1\}$ and $A_2 = \{S_0 \to C \to D \to S_1\}$. 
Let the feasible action set be $\cS = \{A_1, A_2\}.$ The numbers on the edges denote the probability of that edge being unblocked. 
For example, the probability of $C \to D$ being unblocked is $0.8$. 
When we select a path, we get reward $1$ if and only if the path is unblocked and get reward $0$ if the path is blocked somewhere. 
So the optimal action is $A_1$ with expected reward $0.64$ and $A_2$ is suboptimal with expected reward $0.504$.

Next we analyze those times when the learning agent selects path $A_2$ instead of the optimal $A_1$. 
Notice that if the observed edges are $S_0 \to C \to D$ or $S_0 \to C$, we will not abandon $A_2$ because the expected rewards are $0.9 \times 0.8$ and $0.9$, higher than $0.64$. 
Only the times when all edges in $A_2$ being observed will help to recognize $A_2$ and abandon it. 
Recall that the probability of all edges of $A_2$ being observed is $p_{A_2} = 0.9 \times 0.8 = 0.72.$ 
So we have
$$
\EE[N_{A_2}]p_{A_2} \leq \frac{c \log(T)}{\Delta^2},
$$
where $N_{A_2}$ is the number of times that learning agent selects $A_2$ and $\Delta$ is the difference of the best expected reward minus the expected reward of $A_2$.
Therefore,
$$
\EE[N_{A_2}] \leq \frac{c \log(T)}{p_{A_2} \Delta^2}
$$
and
$$
R(T) \leq \EE[\Delta N_{A_2}] \leq \frac{c \log(T)}{p_{A_2} \Delta}.
$$

\appendix

\section{Proof of Theorem~\ref{thm:main}}
